What does the crowd believe? A hierarchical approach to estimating subjective beliefs from empirical data

### 2016-02-01 text/01_CogSci_abstract/paper.tex
minor edits Anthea

More sophisticated \emph{give-a-number} tasks give more information, but can be difficult to
implement and analyze. A prominent method in economics uses \emph{scoring rules}
\citep{Savage1971:Elicitation-of-,AndersenFountain2014:Estimating-Subj,SchlagTremewan2014:A-penny-for-you}. Roughly
put, scoring rules are schemes of rewarding participants' answers that make sure that responses
(by rational participants) faithfully reflect a measure of interest: the actual subjective
probability of an event, the mean of a distribution, a credible interval etc. Scoring-rule
tasks require participants to become sufficiently familiar with the (usually probabilistic)
payoff scheme. Another insightful, but also complex approach is to use a cleverly designed
\emph{iterated learning paradigm} \citep{LewandowskyGriffiths2009:The-Wisdom-of-I}.

@@

Explanatory success aside, the question remains whether mean slider ratings measure
what we would like them to. Are these good approximations of a central tendency of participants'
individual beliefs? Are these measures consistent with participants' behavior in other tasks, such
as \emph{give-a-number}, as well? To address this issue we collected data in a within-subject paradigm 
from three task types: (i) \emph{binned histograms}, (ii) \emph{give-a-number} and (iii)
\emph{paired comparisons}, i.e., a direct comparison of two bins from the \emph{binned
  histograms} task. Using a Bayesian hierarchical model, we used the data from all three
dependent measures to infer likely latent subjective beliefs, where each subjective belief is,
intuitively, a noisy perturbation of a population-level belief. We find that mean \emph{a
  posteriori} population-level beliefs are approximated well by mean slider ratings, suggesting
that the latter may indeed be a plausible, yet cheap measure of what the crowd believes.
Moreover, the model is able to capture participants' behavior in all three task types reasonably
well, suggesting that what mean slider ratings measure is what we think it is: a population-level
central tendency of latent subjective beliefs.

@@

On \emph{binned histogram} (BH) trials, participants saw an item's context sentence and were
asked to \emph{Please rate how likely it is that Y} (where Y corresponded to the appropriate BH
frame in \tableref{tab:Items}). They then adjusted 15 sliders, one per bin, with five points
labeled \emph{impossible}, \emph{not very likely}, \emph{neutral}, \emph{very likely}, and
\emph{extremely likely}. Bins were determined by dividing up the entire interval spanned by the
item's minimum and maximum value into equally sized bins (\tableref{tab:Items}).

>>>>

More sophisticated \emph{give-a-number} tasks give more information, but can be difficult to
implement and analyze. A prominent method in economics uses \emph{scoring rules}
\citep{Savage1971:Elicitation-of-,AndersenFountain2014:Estimating-Subj,SchlagTremewan2014:A-penny-for-you}. Scoring
rules are complex schemes of assigning monetary rewards to participants' answers that make sure
that responses (by rational participants) faithfully reflect a measure of interest: the actual
subjective probability of an event, the mean of a distribution, a credible interval
etc. Scoring-rule tasks require participants to become sufficiently familiar with the (usually
probabilistic) payoff scheme. Another insightful, but also complex approach is to use a
cleverly designed \emph{iterated learning paradigm}
\citep{LewandowskyGriffiths2009:The-Wisdom-of-I}.

@@

Explanatory success aside, the question remains whether mean slider ratings measure what we
would like them to. Are these good approximations of a central tendency of participants'
individual beliefs? Are these measures consistent with participants' behavior in other tasks,
such as \emph{give-a-number}, as well? To address this issue we collected data in a
within-subject paradigm from three task types: (i) \emph{binned histograms}, (ii)
\emph{give-a-number} and (iii) \emph{paired comparisons}, i.e., a direct comparison of two bins
from the \emph{binned histograms} task that included as a further consistency check. Using a
Bayesian hierarchical model, we used the data from all three dependent measures to infer likely
latent subjective beliefs, where each subjective belief is, intuitively, a noisy perturbation
of a population-level belief. We find that mean \emph{a posteriori} population-level beliefs
are approximated well by mean slider ratings, suggesting that the latter may indeed be a
plausible, yet cheap measure of what the crowd believes.  Moreover, the model is able to
capture participants' behavior in all three task types reasonably well, suggesting that what
mean slider ratings measure is what we think it is: a population-level central tendency of
latent subjective beliefs.

@@

On \emph{binned histogram} (BH) trials, participants saw an item's context sentence and were
asked to \emph{Please rate how likely it is that Y} (where $Y$ came from the corresponding BH
frame in \tableref{tab:Items}). They adjusted 15 continuous sliders, one per bin, with five
points labeled \emph{impossible}, \emph{not very likely}, \emph{neutral}, \emph{very likely},
and \emph{extremely likely}. Bins were determined by dividing the interval spanned by
the item's minimum and maximum value into equally sized bins (\tableref{tab:Items}).
